Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2022-02-15 paper/pge_appendix.Rmd
prefix page, figure, and table numbers with A
use dev version of DCPO
update

@@

@@

\pagebreak
# Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism and Their Distribution
```{r egr_summary_stats, cache = TRUE, cache.extra = tools::md5sum(here::here("data-raw", "dcpo_input_raw_public.csv"))}
dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
                                  col_types = "cdcddcd")

@@

>>>>

\renewcommand{\thepage}{A\arabic{page}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

@@

# If development version of `DCPO` is not yet installed:
# remotes::install_github("fsolt/DCPO")

@@

\pagebreak
# Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism and Their Distribution
```{r egr_summary_stats, cache = FALSE, cache.extra = tools::md5sum(here::here("data-raw", "dcpo_input_raw_public.csv"))}
dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
                                  col_types = "cdcddcd")

@@

process_dcpo_input_raw <- function(dcpo_input_raw_df) {
  dcpo_input_raw_df %>% 
    with_min_yrs(2) %>% 
    with_min_cy(5) %>% 
    filter(year >= 1972) %>% 
    group_by(country) %>% 
    mutate(cc_rank = n()) %>% 
    ungroup() %>% 
    arrange(-cc_rank)
}
